\texttt{MSnbase}, efficient and elegant R-based processing and visualisation of raw mass spectrometry data

### 2020-06-26 msnbase2.Rnw
Mention and refer to the Supplementary Information in the main text

In the following sections, we describe \texttt{MSnbase}'s ability to
efficiently handle very large mass spectrometry data and experiments
and how it can be used for data processing and visualisation. We will
also illustrate how it makes use of the forward-pipe operator
(\texttt{\%>\%}) defined in the \texttt{magrittr} package. This
operator has proved useful to develop non-trivial analyses by
combining individual functions into easily readable pipelines.

@@

We have presented here some some important functionality of
\texttt{MSnbase} version 2. The new on-disk infrastructure enables
large scale data analyses~\cite{Nothias:2020}, either using
\texttt{MSnbase} directly or through packages that rely on it, such as
\texttt{xcms}. We have also illustrated how \texttt{MSnbase} can be
used for standard data analysis and visualisation, and how it can be
used for method development and prototyping.

>>>>

In the following sections, we describe \sout{\texttt{MSnbase}'s ability to
  efficiently handle very large mass spectrometry data and experiments and how
  it} \code{red}{how \texttt{MSnbase}} can be used for data processing and
visualisation. We will also illustrate how it makes use of the forward-pipe
operator (\texttt{\%>\%}) defined in the \texttt{magrittr} package. This
operator has proved useful to develop non-trivial analyses by combining
individual functions into easily readable pipelines. \code{red}{An example for
  \texttt{MSnbase}'s ability to efficiently handle also very large mass
  spectrometry experiments (in this case with 5,773,464 spectra in 1,182 mzXML
  files) is provided as Supplementary Information.}

@@

We have presented here some important functionality of
\texttt{MSnbase} version 2. The new on-disk infrastructure enables
large scale data analyses~\cite{Nothias:2020}, either using
\texttt{MSnbase} directly or through packages that rely on it, such as
\texttt{xcms}. We have also illustrated how \texttt{MSnbase} can be
used for standard data analysis and visualisation, and how it can be
used for method development and prototyping.
